analysis-pilot

### 2023-08-19 code/analysis-pilot.Rmd
image accuracy

ggplot(data = accuracy, aes(x = image, y = percent)) +
  geom_bar(stat = "identity", position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  geom_smooth(method="lm")+
  theme_classic() +
  xlab("\nTarget") +
  ylab("Percent accuracy\n") +
  #scale_x_continuous(breaks=seq(1,12,1)) +
  scale_y_continuous(breaks=seq(0,100,10), limits = c(0, 100), expand=c(0,0)) +
  geom_text(aes(label = percent), vjust = 1.7, color = "white", size = 3) +
  theme(aspect.ratio = 4/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.position = "none")
ggsave("AccuracybyTarget.png")
```

>>>>

ggplot(data = accuracy, aes(x = image, y = percent)) +
  geom_bar(stat = "identity", position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  geom_smooth(method="lm")+
  theme_classic() +
  xlab("\nTarget") +
  ylab("Percent accuracy\n") +
  #scale_x_continuous(breaks=seq(1,12,1)) +
  scale_y_continuous(breaks=seq(0,100,10), limits = c(0, 100), expand=c(0,0)) +
  geom_text(aes(label = percent), vjust = 1.7, color = "white", size = 3) +
  theme(aspect.ratio = 4/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.position = "none")
ggsave("AccuracybyTarget.png")
```
#accuracy of each image over time
```{r}
accuracy <- filtered_data %>% 
  mutate(image = case_when(
  target == "/experiment/B1.jpg" ~ "Walking",
  target == "/experiment/D1.jpg" ~ "Lying",
  target == "/experiment/E1.jpg" ~ "Jumping",
  target == "/experiment/I1.jpg" ~ "Holding",
)) %>% 
  mutate(trialNum = index-1) %>% 
  filter(!index %in% c(0, 1)) %>%
  group_by(image, index) %>% 
  summarize(total=n(),
            correct=sum(countCorrect)) %>%
  mutate(fraction = correct/total*100, percent = signif(fraction, 2)) %>% 
  filter(image == "Walking")

ggplot(accuracy, aes(x = index-1, y = percent)) +
  geom_line(aes(group=image)) +
  labs(color = "Tangram", x = "\nTrial", y = "Percent accuracy\n") +
  scale_x_continuous(breaks=seq(1,12,1), limits = c(1,12)) +
  scale_y_continuous(breaks=seq(0,100,10), limits = c(0,100)) +
  theme_classic() +
  theme(aspect.ratio = 7/9,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.title=element_text(size=13,face="bold"),
        legend.text=element_text(size=9),
        legend.position="right")

ggsave("WalkingAccuracybyTarget.png")
```
